%-------------------------
% Resume in Latex
% Author : Pranav Kumar
% Based off of: https://github.com/pranav083/resume_latex
% License : MIT
%------------------------


\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  % \vspace{-4pt}\scshape\raggedright\large
  \centering\scshape\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Pranav \textbf{Kumar}} \\ \vspace{1pt}
    \href{https://pranav083.github.io/}{\underline{Personal-Site}} $|$
    \href{mailto:pranavkumar083@proton.me}{\underline{pranavkumar083@proton.me}} $|$
    \href{https://linkedin.com/in/pranav083}{\underline{linkedin.com/in/pranav083}} $|$
    \small{\underline{+91-9614436659}}   
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {UIET, Panjab University}{Chandigarh, IN}
      % {B.E in Electronics and Communication Engineering }{\textit{CGPA: 7.3} May 2016 -- Sept. 2020}
      {B.E in Electronics and Communication Engineering }{May 2016 -- Sept. 2020}

    \resumeSubheading
      {Delhi Public School}{Ranchi, IN}
      {Higher Secondary, CBSE }{\textit{90.2 \%} May 2015}
  \resumeSubHeadingListEnd

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RELEVANT COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Relevant Coursework}

\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item \hspace{0pt}{
   \hspace{-4pt}{Basic Electronic Devices and Circuits, Operating Systems, Computer Architecture, 
   Data Structure and Algorithm, Microprocessors and Microcontrollers,  Digital Electronics, Verilog, System Verilog, Linear Integrated Circuits
   and its Applications (IC),  Switching Theory and Logical Design, Pulse and Digital Circuits(PDC),
   Power Electronics, Electro Magnetic Fields, Power Electronic Controller Drives, Digital Signal
   Processing (DSP),Digital Control Systems} \\
  }}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH INTEREST
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Research Interest}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item \hspace{0pt}{
   \hspace{-4pt}{Electronic Devices and Circuits, Digital Electronics, Robotics,Autonomous systems design, Robotics, Computer Architecture for a variety of emerging Applications, Programmable Logic (FPGA), Embedded System
   Design, Computer Hardware Design,  Switching Theory and Logical Design, Microprocessors and Microcontrollers, Programming Power Electronic Controller Drives, Digital Control Systems} \\
  }}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Job / Research Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
    {ARTPARK @IISc, Bangalore}{Arm4, BLDC-drivers, STM32, TI, CAN, FOC, ROS}
    {Embedded System Engineer}{May 2023 -- Present , Bangalore, IN}
    \resumeItemListStart
      \resumeItem{Working Under Supervision of \textbf{Prof. Shishir N. Y. Kolathaya}}
      \resumeItem{Development of System design of Quadruped robot.}
      \resumeItem{Development of firmware and hardware of legged robot.}
      \resumeItem{Responsible for the development of Communication stack of robot.}
    \resumeItemListEnd

    \resumeSubheading
    {Flux Auto Pvt. Ltd.}{ARMm7, FreeRTOS, EclipseIDE, STM32, TI, BLDC, CAN, I2C, ROS}
    {Embedded System Engineer}{June 2021 -- March 2023, Bangalore, IN}
    \resumeItemListStart
      \resumeItem{Development of Generic solution for making retrofit kit for vehicle to make it autonomous.}
      \resumeItem{Worked on Software and Hardware solution for Off-road and Industrial vehicle.}
      \resumeItem{Working with embedded systems to have complete deployable system on device.}
      \resumeItem{Development on multi-node decentralize CAN system for Off-Road vehicle.}
      \resumeItem{Development on autonomous system for Industrial vehicle (Fork-lift, BOPT etc.)}
      \resumeItem{Worked on different motor with heavy torque and precision.}
      \resumeItem{Writting library and driver for different ICs.}
    \resumeItemListEnd
    
    \resumeSubheading
      {Futuristic Labs Pvt. Ltd.}{ARMm4, FreeRTOS, esp-idf, OpenCV, Stepper, I2C, UART, Docker, Mqtt}
      {Embedded Firmware Engineer}{Jan. 2020 -- March 2021, Hyderabad, IN}
      \resumeItemListStart
        \resumeItem{Worked on autonomous cooking Machine(for Indian Cusine) Firmware and embedded design}.
        \resumeItem{Development of embedded solution form different Hardware and IOT based appliances. }
        \resumeItem{Development of bridge between RTOS Board and Compute Module. }
        \resumeItem{Working with embedded systems with safety constrain in it realted to thermal etc.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd    
% -----------Multiple Positions Heading-----------
  %  \resumeSubSubheading
  %   {Software Engineer I}{Oct 2014 - Sep 2016}
  %   \resumeItemListStart
  %      \resumeItem{Apache Beam}
  %        {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
  %   \resumeItemListEnd
  % % \resumeSubHeadingListEnd
%-------------------------------------------
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Internship}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Google Summer Of Code(GSOC)}{Device Tree, Kernel Module, PRU, ARMa8, Embedded C}
      {BeagleBoard.Org(Open Source Contributer) }{June $-$ Aug. 2019, Chandigarh, IN}
      \resumeItemListStart
        \resumeItem{Using BeagleBone and 74hc299 shift Register, provided a reference design for bi-directional commincation for multiple peripherials.}
        \resumeItem{For more Infomation see Project \textbf{\href{https://elinux.org/Beagleboard_gsoc_2019_bi-directional_progress}{\underline{Page}}} and Beaglebone official blog \textbf{\href{https://beagleboard.org/blog/2019-06-02-beagleboard-org-community-kicks-off-gsoc-2019-with-four-projects}{\underline{Page}}}.}
        \resumeItem{Youtube \textbf{\href{https://www.youtube.com/watch?v=ZZDT6jNslqw&list=PLttoix_9Us2yHM4zNr08ynm4iwXZTgxam}{\underline{Playlist}}} and Github \textbf{\href{https://github.com/pranav083/pocket_beagle-work}{\underline{Code}}}.}
    \resumeItemListEnd

    \resumeSubheading
      {e-YRC (IIT Bombay)}{OpenCV, C++, Rpi, Atmel, i2c, FSM}
      {Team Leader \& Open Source Contributer}{Oct. 2018 $-$ Feb. 2019, Chandigarh, IN}
      \resumeItemListStart
        \resumeItem{Making a lighter and less complex multifunctional line Following algorithm using FSM(Finite State Machine).}
        \resumeItem{Using OpenCV for object Detection and ArUco Markers. }
        \resumeItem{Follow the links Youtube \textbf{\href{https://youtu.be/RxFSsqW_D48}{\underline{Video}}} and Github \textbf{\href{https://github.com/pranav083/FSM_code}{\underline{Code}}}.}
      \resumeItemListEnd

    \resumeSubheading
    {Embedded Product development for Saksham Creative Edu.(NGO)}{Atmel, I2C, Team Managing}
    {Student Lead }{Sept.$-$ Dec. 2018, Chandigarh, IN}
    \resumeItemListStart
      \resumeItem{Worked as Embedded designer in the team.}
      \resumeItem{Designed and build several embedded based product for NGO by managing resourses}
      \resumeItem{Team of around 20 team members.Follow up this Github Link for More Info \textbf{\href{https://github.com/pranav083/Tinkering_project}{\underline{Codes and Document}}}.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Projects}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{* Stepper$\_$STSPIN220$-$library} $|$ \emph{C++, Arduino IDE, Driver, STSPIN220}}{Dec. 2020}
          \resumeItemListStart
            \resumeItem{Development of the generic driver for 1/256 steps stepper driver Blog and Code \underline{\textbf{\href{https://pranav083.github.io/post/stepper_stspin220/}{Link}}}.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{* QuadCopter PX4 ROS} $|$ \emph{MavROS, ROS, Python, Git }}{Oct. 2019}
          \resumeItemListStart
            \resumeItem{worked on the simulation of the px4 drones using Mavros and Mavlink in ROS and Gazebo \underline{\textbf{\href{https://github.com/pranav083/Ros_projects}{Link}}}.}
          \resumeItemListEnd
      % \resumeProjectHeading
      % {\textbf{* CAN-BUS Debugging$-$Blog} $|$ \emph{C++, Arduino IDE, Driver, STSPIN220}}{Dec. 2020}
      % \resumeItemListStart
      %   \resumeItem{How to debug a CAN Based system Blog and Code \underline{\textbf{\href{https://pranav083.github.io/}{Link}}}.}
      % \resumeItemListEnd
    \resumeSubHeadingListEnd


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROGRAMMING SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Technical Skills}\vspace{-2pt}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C/C++, Python, Embedded C, OpenCV, Embedded Linux, Linux} \\
     \textbf{Hardware Tools}{: ARM, I2C, SPI, CAN, Modbus, UART, BeagleBone, Compute Modules(Rpi CM4),  ESP32} \\
     \textbf{Developer Tools}{: Git, Docker, TravisCI, LvGL, MqTT, ROS, FreeRTOS} \\
     \textbf{Hardware }{: STM32H7x, STM32G4x, TI, Steppers, BLDC, FOC etc.} \\
     \textbf{Familiar}{: Algorithms, \LaTeX, Shell, Yocto, ESP-IDF}
    }}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Achievements
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Achievements And Awards}\vspace{-2pt}
  \begin{itemize}
    \item \vspace{-0pt}{2019  $-$ Robot Operating System Conference \textbf{ROSCon-19, Macau, China Scholarship Holder}}
    \item \vspace{-9pt}{2019  $-$  Awardee for excellence in Technology field by \textbf{Mrs. Kirron Kher (MP ,Chandigarh)}}    
    \item \vspace{-9pt}{2019  $-$  Got \textbf{1st} Award at Design and Idea Competition by IIC, Panjab University at Chandigarh}   
    \item \vspace{-9pt}{2019  $-$  \textbf{Mentor} of winning team at \textbf{Smart India Hackathon-2019} by  \underline{\textbf{\href{https://www.kokuyocamlin.com/}{Kokuyo Camlin}}} at IIT Hyd.}  
    % \item \vspace{-9pt}{2019	$-$  Poster presentation at Chandigarh Science Congress(CHESCON)}   
    \item \vspace{-9pt}{2018	$-$  Winner of Pocket Beagle at \textbf{Mouser electronics} event in \textbf{IIT Roorkee} }
  \end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Organization And Events
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Community And Events }
  \begin{itemize}
    \item \vspace{-0pt}{2018 $\&$ 2019 Speaker at \underline{\textbf{\href{https://www.softwarefreedomday.in/Archive}{Software Freedom Day}}},Panjab University } 
    \item \vspace{-9pt}{Speaker \& Organizer in Embbeded Community in the Chandigarh Area, See \textit{\textbf{\href{https://drive.google.com/drive/folders/1DxT2_Fzj40LQEiOTwckY73_On0V8weF_?usp=sharing}{\underline{Gallery Link}}}}.}
    \item \vspace{-9pt}{Community Head of Embedded Telegram Group : \underline{\textbf{\href{https://t.me/rosandrobotic}{Link}}}}
    \item \vspace{-9pt}{Poster presentation on FSM at Chandigarh Science Congress (\textbf{CHESCON})}
  \end{itemize} 
  %-------------------------------------------
  \begin{itemize}[leftmargin=0.15in, label={}]
     \small{\item \hspace{-10pt}{
      \textbf{Note}{: All the \textbf{\underline{Underline}} text are Clickable Links.} \\
     }}
 \end{itemize}
\end{document}
