%-------------------------
% Resume in Latex
% Author : Pranav Kumar
% Based off of: https://github.com/pranav083/resume_latex
% License : MIT
%------------------------


\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  % \vspace{-4pt}\scshape\raggedright\large
  \centering\scshape\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Pranav \textbf{Kumar}} \\ \vspace{1pt}
    \href{https://pranav083.github.io/}{\underline{Personal-Site}} $|$
    \href{mailto:pranavkumar083@proton.me}{\underline{pranavkumar083@proton.me}} $|$
    \href{https://linkedin.com/in/pranav083}{\underline{linkedin.com/in/pranav083}} $|$
    \small{\underline{+1-540-934-8078}} $|$
    \small{ Virginia, USA}   
\end{center}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Job / Research Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
    {ARTPARK @IISc, Bangalore}{Arm4, BLDC-drivers, STM32, TI, CAN, FOC, ROS}
    {Embedded System Engineer}{May 2023 -- July 2024 , Bangalore, IN}
    \resumeItemListStart
      \resumeItem{Working Under Supervision of \underline{\textbf{\href{https://eecs.iisc.ac.in/people/shishir-kolathaya/}{Asst. Prof. Shishir N. Y. Kolathaya}}}}
      \resumeItem{Development of System design of Quadruped robot.}
      \resumeItem{Development of firmware and hardware of legged robot.}
      \resumeItem{Responsible for the development of Communication stack of robot.}
      \resumeItem{Worked with team on the development of BLDC motor driver of Actuator.}
    \resumeItemListEnd

    \resumeSubheading
    {Flux Auto Pvt. Ltd.}{ARMm7, FreeRTOS, EclipseIDE, STM32, TI, BLDC, CAN, I2C, ROS}
    {Embedded System Engineer}{June 2021 -- March 2023, Bangalore, IN}
    \resumeItemListStart
      \resumeItem{Development of Generic solution for making retrofit kit for vehicle to make it autonomous.}
      \resumeItem{Worked on Software and Hardware solution for Off-road \underline{\textbf{\href{https://youtu.be/TS1C2sPgFIc}{Tractor}}} and Industrial vehicle.}
      \resumeItem{Working with embedded systems to have complete deployable system on device.}
      \resumeItem{Development on multi-node decentralize CAN system for Off-Road vehicle.}
      \resumeItem{Development on autonomous system for Industrial vehicle (Fork-lift, BOPT etc.)}
      % \resumeItem{Worked on different motor with heavy torque and precision.}
      \resumeItem{Writting library and driver for different ICs.}
    \resumeItemListEnd
    
    \resumeSubheading
      {Futuristic Labs Pvt. Ltd.}{ARMm4, FreeRTOS, esp-idf, OpenCV, Stepper, I2C, UART, Docker, Mqtt}
      {Embedded Firmware Engineer}{Jan. 2020 -- May 2021, Hyderabad, IN}
      \resumeItemListStart
        \resumeItem{Worked on autonomous cooking Machine(for Indian Cusine) Firmware and embedded design}.
        \resumeItem{Development of embedded solution form different Hardware and IOT based appliances. }
        \resumeItem{Development of bridge between RTOS Board and Compute Module. }
        \resumeItem{Working with embedded systems with safety constrain in it realted to thermal etc.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd    
% -----------Multiple Positions Heading-----------
  %  \resumeSubSubheading
  %   {Software Engineer I}{Oct 2014 - Sep 2016}
  %   \resumeItemListStart
  %      \resumeItem{Apache Beam}
  %        {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
  %   \resumeItemListEnd
  % % \resumeSubHeadingListEnd
%-------------------------------------------
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROGRAMMING SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Technical Skills}\vspace{-2pt}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C/C++, Python, Embedded C, OpenCV, Embedded Linux, Linux} \\
     \textbf{Hardware Protocols}{: ARM, I2C, SPI, CAN, Modbus, UART, BeagleBone, Compute Modules(Rpi CM4),  ESP32} \\
     \textbf{Developer Tools}{: Git, Docker, TravisCI, LvGL, MqTT, ROS, FreeRTOS} \\
     \textbf{Hardware }{: STM32H7x, STM32G4x, TI, Steppers, BLDC, FOC, Xilinx FPGA Spartan etc.} \\
     \textbf{Familiar}{: Algorithms, \LaTeX, Shell, Yocto, ESP-IDF}
    }}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}
  \resumeSubHeadingListStart
% Virginia tech 
    \resumeSubheading
      {Virginia Tech}{Virginia, USA}
      {MS in Computer Engineering }{3.9/4 GPA August 2024 -- May 2026}

% UIET, Panjab University, Chandigarh      
    \resumeSubheading
      {UIET, Panjab University}{Chandigarh, IN}
      % {B.E in Electronics and Communication Engineering }{\textit{CGPA: 7.3} May 2016 -- Sept. 2020}
      {B.E in Electronics and Communication Engineering }{ May 2016 -- Sept. 2020}

%    \resumeSubheading
%      {Delhi Public School}{Ranchi, IN}
%      {Higher Secondary, CBSE }{\textit{90.2 \%} May 2015}
  \resumeSubHeadingListEnd

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RELEVANT COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Relevant Coursework}

\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item \hspace{0pt}{
   \hspace{-4pt}{Basic Electronic Devices and Circuits, Operating Systems, Computer Architecture, 
   Data Structure and Algorithm, Microprocessors and Microcontrollers,  Digital Electronics, Verilog, Linear Integrated Circuits
   and its Applications (IC),  Switching Theory and Logical Design,
   Digital Signal, Computer Network, Processing (DSP),Digital Control Systems} \\
  }}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH INTEREST
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Research Interest}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item \hspace{0pt}{
   \hspace{-4pt}{Autonomous systems design, Electronic Devices and Circuits, Digital Electronics, Robotics,  Computer Architecture for a variety of emerging Applications, Programmable Logic (FPGA), Embedded System
   Design, Computer Hardware Design,  Switching Theory and Logical Design, Microprocessors and Microcontrollers, Programming Electronic Controller Drives, Digital Control Systems} \\
  }}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     INTERNSHIP/ LONG PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Internship/Long Term Project}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Google Summer Of Code(GSOC)}{Device Tree, Kernel Module, PRU, ARMa8, Embedded C}
      {BeagleBoard.Org(Open Source Contributer) }{June $-$ Aug. 2019, Chandigarh, IN}
      \resumeItemListStart
        \resumeItem{Using BeagleBone and 74hc299 shift Register, provided a reference design for bi-directional commincation for multiple peripherials.}
        \resumeItem{For more Infomation see Project \textbf{\href{https://elinux.org/Beagleboard_gsoc_2019_bi-directional_progress}{\underline{Page}}} and Beaglebone official blog \textbf{\href{https://beagleboard.org/blog/2019-06-02-beagleboard-org-community-kicks-off-gsoc-2019-with-four-projects}{\underline{Page}}}.}
        \resumeItem{Youtube \textbf{\href{https://www.youtube.com/watch?v=ZZDT6jNslqw&list=PLttoix_9Us2yHM4zNr08ynm4iwXZTgxam}{\underline{Playlist}}} and Github \textbf{\href{https://github.com/pranav083/pocket_beagle-work}{\underline{Code}}}.}
    \resumeItemListEnd

    \resumeSubheading
    {Embedded Product development for Saksham Creative Edu.(NGO)}{Atmel, I2C, Team Managing}
    {Student Coordinator }{Sept.$-$ Dec. 2018, Chandigarh, IN}
    \resumeItemListStart
      \resumeItem{Worked as Embedded designer in the team.}
      \resumeItem{Designed and build several embedded based product for NGO by managing resourses}
      \resumeItem{Team of around 20 team members.Follow up this Github Link for More Info \textbf{\href{https://github.com/pranav083/Tinkering_project}{\underline{Codes and Document}}}.}
      \resumeItemListEnd


    \resumeSubheading
    {CIC, University Of Delhi}{Atmel, SPI, NRF communication}
    {Team member \& Intern}{June 2018 – July 2018 , Delhi, India}
    \resumeItemListStart
    \resumeItem{Worked on swarm formation control robots using ROS(robot operating system).}
    \resumeItem{Designed and build several embedded based swarm board for intercommunication.}
    \resumeItem{Follow the \textbf{\href{http://crip.ml}{\underline{link}}} for more  Information and Achieved work \textbf{\href{https://github.com/pranav083/ROS_work_earlier_nrf}{\underline{Code}}.}}
    \resumeItemListEnd 



    % \resumeSubheading
    % {Design and Innovation Center}{Atmel, SPI, NRF communication}
    % {Team Leader}{Jan 2017 - May 2017 , PU,Chandigarh, India}
    % \resumeItemListStart
    % % \resumeItem{\textbf{Contact :} Dr. Naveen Aggarwal - \textit{\href{mailto:navagg@pu.ac.in}{\textbf{navagg@pu.ac.in}}}}
    % \resumeItem{Initiative By MHRD(Gov.of India) on collaborative research and innovation}
    % \resumeItem{Proposed a 3-D printing technology with the multipurpose
    % capabilities enabling us to multi tasking like 2D plotting, 3D printing etc.}
    % \resumeItem{Enabled Multiple capabiltiy with only addon modules with same Base .}

    % \resumeItem{Follow the \textbf{\href{http://crip.ml}{\underline{link}}} for more  Information and Achieved work \textbf{\href{https://github.com/pranav083/ROS_work_earlier_nrf}{\underline{Code}}.}}
    % \resumeItemListEnd 

  \resumeSubHeadingListEnd

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH PAPER
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Research Work}

\resumeSubHeadingListStart

\resumeProjectHeading
    {\textbf{* Poster Presentation }}{Mar. 2019}
    \resumeItemListStart
      \resumeItem{Line Following Algorithms using Finite State Machine at Chandigarh Science Congress (\textbf{CHESCON})}
    \resumeItemListEnd
\resumeProjectHeading
    {\textbf{* Research Paper}}{Nov. 2023}
    \resumeItemListStart
      \resumeItem{"Autonomous System of Heavy Vehicle Using CAN Networking" \underline{\textbf{\href{https://doi.org/10.1007/978-981-97-7616-0_7}{Link}}} at {\textbf{ICDEMI}}, Bangalore through Springer} 
    \resumeItemListEnd
\resumeSubHeadingListEnd 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Projects}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{* Stepper$\_$STSPIN220$-$library} $|$ \emph{C++, Arduino IDE, Driver, STSPIN220}}{Dec. 2020}
          \resumeItemListStart
            \resumeItem{Development of the generic driver for 1/256 steps stepper driver Blog and Code \underline{\textbf{\href{https://pranav083.github.io/post/stepper_stspin220/}{Link}}}.}
          \resumeItemListEnd

      \resumeProjectHeading
      {\textbf{* e-YRC (IIT Bombay)} $|$ \emph{OpenCV, C++, Rpi, Atmel, i2c, FSM}}{Oct. 2018 - Feb. 2019}
      \resumeItemListStart
        \resumeItem{Making a lighter and less complex multifunctional line Following algorithm using FSM(Finite State Machine).}
        \resumeItem{Follow the links Youtube \textbf{\href{https://youtu.be/RxFSsqW_D48}{\underline{Video}}} and Github \textbf{\href{https://github.com/pranav083/FSM_code}{\underline{Code}}}.}
      \resumeItemListEnd


      % \resumeProjectHeading
      % {\textbf{* QuadCopter PX4 ROS} $|$ \emph{MavROS, ROS, Python, Git }}{Oct. 2019}
      % \resumeItemListStart
      %   \resumeItem{worked on the simulation of the px4 drones using Mavros and Mavlink in ROS and Gazebo \underline{\textbf{\href{https://github.com/pranav083/Ros_projects}{Link}}}.}
      % \resumeItemListEnd     https://www.youtube.com/shorts/vt06KxWhGN4
      
      \resumeProjectHeading
      {\textbf{* 3D/2D Printer} $|$ \emph{Marlin, Atmel, Stepper, Embedded C}}{Jan 2017 - May 2017}
      \resumeItemListStart
        \resumeItem{Proposed a 3-D printing technology with the multipurpose  capabilities like 2D plotting, 3D printing etc. through addon modules, \textbf{\href{https://www.youtube.com/shorts/vt06KxWhGN4}{\underline{Video}}} and Github \textbf{\href{https://github.com/pranav083/Modular_printer}{\underline{Code}}}.}
      \resumeItemListEnd   

      % \resumeSubheading
          % {e-YRC (IIT Bombay)}{OpenCV, C++, Rpi, Atmel, i2c, FSM}
          % {Team Leader \& Open Source Contributer}{Oct. 2018 $-$ Feb. 2019, Chandigarh, IN}
          % \resumeItemListStart
          %   \resumeItem{Making a lighter and less complex multifunctional line Following algorithm using FSM(Finite State Machine).}
          %   \resumeItem{Using OpenCV for object Detection and ArUco Markers. }
          %   \resumeItem{Follow the links Youtube \textbf{\href{https://youtu.be/RxFSsqW_D48}{\underline{Video}}} and Github \textbf{\href{https://github.com/pranav083/FSM_code}{\underline{Code}}}.}
          % \resumeItemListEnd          
      % \resumeProjectHeading
      % {\textbf{* CAN-BUS Debugging$-$Blog} $|$ \emph{C++, Arduino IDE, Driver, STSPIN220}}{Dec. 2020}
      % \resumeItemListStart
      %   \resumeItem{How to debug a CAN Based system Blog and Code \underline{\textbf{\href{https://pranav083.github.io/}{Link}}}.}
      % \resumeItemListEnd
    \resumeSubHeadingListEnd




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Achievements
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Achievements And Awards}\vspace{-2pt}
  \begin{itemize}
    \item \vspace{-0pt}{2019  $-$ Robot Operating System Conference \textbf{ROSCon-19, Macau, China Scholarship Holder}}
    \item \vspace{-9pt}{2019  $-$  Awardee for excellence in Technology field by \textbf{Mrs. Kirron Kher (MP ,Chandigarh)}}    
    \item \vspace{-9pt}{2019  $-$  Got \textbf{1st} Award at Design and Idea Competition by IIC, Panjab University at Chandigarh}   
    \item \vspace{-9pt}{2019  $-$  \textbf{Mentor} of winning team at \textbf{Smart India Hackathon-2019} by  \underline{\textbf{\href{https://www.kokuyocamlin.com/}{Kokuyo Camlin}}} at IIT Hyd.}  
    % \item \vspace{-9pt}{2019	$-$  Poster presentation at Chandigarh Science Congress(CHESCON)}   
    \item \vspace{-9pt}{2018	$-$  Winner of Pocket Beagle at \textbf{Mouser electronics} event in \textbf{IIT Roorkee} }
    \item \vspace{-9pt}{2021-2022	$-$  Three times winner of Best Employee per Quarter at \textbf{Flux Auto} }
  \end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Organization And Events
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Community , Events And Volunteer Work }
  \begin{itemize}
    \item \vspace{-0pt}{Organised Hackathon for straight Three Years \underline{\textbf{\href{https://drive.google.com/file/d/19Fp3vJ5HSwA1xKMzz02ts9GPaJx9FrZb/view?usp=sharing}{Certificate Page: 1-3}}}}
    \item \vspace{-9pt}{2018 $\&$ 2019 Speaker at \underline{\textbf{\href{https://www.softwarefreedomday.in/Archive}{Software Freedom Day}}},Panjab University } 
    \item \vspace{-9pt}{Speaker \& Organizer in Embbeded Community in the Chandigarh Area, See \textit{\textbf{\href{https://drive.google.com/drive/folders/1DxT2_Fzj40LQEiOTwckY73_On0V8weF_?usp=sharing}{\underline{Gallery Link}}}}.}
    \item \vspace{-9pt}{In 2018 Volunteer at TECHNOCIAN Championship \underline{\textbf{\href{https://drive.google.com/file/d/19Fp3vJ5HSwA1xKMzz02ts9GPaJx9FrZb/view?usp=sharing}{Certificate Page : 4}}}}
    \item \vspace{-9pt}{Community Head of Embedded Telegram Group : \underline{\textbf{\href{https://t.me/rosandrobotic}{Link}}}}
    \item \vspace{-9pt}{Student Lead of College Eyantra Robotics Lab for 2.5 years}
    \item \vspace{-9pt}{Regular participant of voluntary Blood Donation Camp}
    % \item \vspace{-9pt}{Poster presentation on FSM at Chandigarh Science Congress (\textbf{CHESCON})}

  \end{itemize} 
  %-------------------------------------------
  \begin{itemize}[leftmargin=0.15in, label={}]
     \small{\item \hspace{-10pt}{
      \textbf{Note}{: All the \textbf{\underline{Underline}} text are Clickable Links.} \\
     }}
 \end{itemize}
\end{document}
