\documentclass[11pt,a4paper]{moderncv}
\moderncvstyle{classic}
\moderncvcolor{blue}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.85]{geometry}

\name{Pranav}{Kumar}
\address{Virginia, USA}{}
\phone[mobile]{+1~(540)~934~8078}
\email{pranavkumar@vt.edu}
\homepage{pranav083.github.io}
\social[linkedin]{pranav083}
\social[github]{pranav083}

\begin{document}

\makecvtitle

\section{Summary}
Embedded Systems Engineer with 4+ years of experience in firmware development, real-time systems, and low-level hardware integration. Passionate about optimizing embedded architectures for performance and efficiency. Strong expertise in C/C++, RTOS, and kernel development.

\section{Technical Skills}
\cvitem{Languages}{C, C++, Python, Linux, LLVM, Compiler}
\cvitem{Protocols}{ARM, I2C, SPI, CAN, UART, BoneBone, Raspberry Pi, ESP32}
\cvitem{Tools}{Git, Docker, ROS, FreeRTOS, AUTOSAR, LLVM}
\cvitem{Hardware}{STM32HF7x, TI, Steppers, BLDC, FOC, Xilinx FPGA Spartan}
\cvitem{Familiar}{Algorithms, \LaTeX, Shell, Parallel Programming}

\section{Education}
\cventry{Aug 2024 -- May 2026}{MS in Computer Engineering}{Virginia Tech}{Virginia, USA}{}{
GPA: 3.9 / 4\\
Coursework: Compiler Optimization, Multiprocessor Programming
}
\cventry{May 2016 -- Sep 2020}{B.E in Electronics and Communication Engineering}{UIET, Panjab University}{Chandigarh, India}{}{}

\section{Experience}
\cventry{Dec 2024 -- Present}{Graduate Student Researcher}{SSRG Lab @Virginia Tech}{Virginia, USA}{}{
\begin{itemize}
\item Developing an indirect call mechanism for binary decompilation under Prof. Binoy Ravindran.
\item Exploring kernel-level instrumentation and code optimization.
\end{itemize}
}
\cventry{May 2023 -- Jul 2024}{Embedded System Engineer}{ARTPARK @IISc}{Bangalore, India}{}{
\begin{itemize}
\item Designed low-level drivers and communication stacks for quadruped robotics.
\item Developed firmware for motor controllers (FOC, BLDC).
\item Implemented high-speed CAN protocols for real-time embedded Linux systems.
\end{itemize}
}
\cventry{Jun 2021 -- Mar 2023}{Embedded System Engineer}{Flux Auto Pvt. Ltd.}{Bangalore, India}{}{
\begin{itemize}
\item Enhanced peripheral drivers for autonomous vehicles.
\item Designed firmware for multi-node CAN networks.
\item Developed RTOS-based firmware and system architecture.
\end{itemize}
}
\cventry{Jan 2020 -- May 2021}{Embedded Firmware Engineer}{Futuristic Labs Pvt. Ltd.}{Hyderabad, India}{}{
\begin{itemize}
\item Developed device drivers and firmware abstraction layers for IoT systems.
\item Built kernel-space and user-space communication bridges.
\item Optimized interrupt-driven firmware for responsiveness and efficiency.
\end{itemize}
}

\section{Projects}
\cventry{Jun 2019 -- Aug 2019}{Google Summer of Code}{BeagleBoard.Org}{Chandigarh, India}{}{
\begin{itemize}
\item Used BeagleBone and 74hck299 to design a bi-directional communication system.
\end{itemize}
}

\section{Achievements}
\cvitem{2019}{ROSCon-19 Scholarship: Attendee at ROSCon-19, Macau, China.}
\cvitem{2019}{Excellence in Technology Award by Mrs. Kirron Kher, MP Chandigarh.}
\cvitem{2019}{1st Prize, Design and Idea Competition, IIC, Panjab University.}
\cvitem{2019}{Mentor of winning team at Smart India Hackathon-2019.}
\cvitem{2021-2022}{Three-time Best Employee of the Quarter, Flux Auto.}

\end{document}
